---
title: "Report: Testing hybrid vigor in the lab in response to Eimeria"
author: "Alice"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    toc: yes
    toc_depth: '4'
    fig_caption: yes        
    includes:  
      in_header: preamble-latex.tex
  word_document:
    toc: yes
    toc_depth: 4
    fig_caption: yes        
    includes:  
      in_header: preamble-latex.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../R/dataPreparation.R")
source("../R/functions.R")
```

# Expe_001, March 2017, Francisca's experiment. infection with E64 and Eflab

## 1. Weight loss
```{r weightalong, echo=FALSE, warning=FALSE, fig.width = 12, fig.height = 5, fig.cap="\\label{fig:weightalong} Weight along the infection experiment"}
plotWeightAlongInf(ExpeDF_001, ylim = c(80, 110))
```

```{r weightalongsum, echo=FALSE, warning=FALSE, fig.width = 12, fig.height = 5, fig.cap="\\label{fig:weightalongsum} Weight along the infection experiment, mean and 95% CI"}
plotWeightAlongInfSUM(ExpeDF_001, ylim = c(80, 110))
```

## 2. Parasite shedding

```{r OPGalong1, echo=FALSE, warning=FALSE, fig.width = 12, fig.height = 10, fig.cap="\\label{fig:OPGalong1} Oocysts shedding along the infection experiment"}
plotOPGAlongInf(ExpeDF_001)
```

```{r OPGalongsum1, echo=FALSE, warning=FALSE, fig.width = 12, fig.height = 10, fig.cap="\\label{fig:OPGalongsum1} Oocysts shedding along the infection experiment, mean and 95% CI"}
plotOPGAlongInfSUM(ExpeDF_001)
```

## 3. Comparison host/parasite proxy

```{r plotComp1, echo=FALSE, warning=FALSE, fig.width = 12, fig.height = 10, fig.cap="\\label{fig:plotComp1} Weight as a function of OPG"}
plotCompOPGWeight(ExpeDF_001)
```

# Expe_003, April-May 2018, first batch Parental strains (F0) BUSNA, STRA, SCHUNT, PWD, infection with Eferrisi (E64 and E139)

## 1. Weight loss

```{r weightalong3, echo=FALSE, warning=FALSE, fig.width = 12, fig.height = 10, fig.cap="\\label{fig:weightalong3} Weight along the infection experiment"}
plotWeightAlongInf(ExpeDF_003, ylim = c(85, 120))
```

```{r weightalongsum3, echo=FALSE, warning=FALSE, fig.width = 12, fig.height = 10, fig.cap="\\label{fig:weightalongsum3} Weight along the infection experiment, mean and 95% CI"}
plotWeightAlongInfSUM(ExpeDF_003, ylim = c(85, 120))
```

## 2. Parasite shedding

```{r OPGalong3, echo=FALSE, warning=FALSE, fig.width = 12, fig.height = 10, fig.cap="\\label{fig:OPGalong3} Oocysts shedding along the infection experiment"}
plotOPGAlongInf(ExpeDF_003)
```

```{r OPGalongsum3, echo=FALSE, warning=FALSE, fig.width = 12, fig.height = 10, fig.cap="\\label{fig:OPGalongsum3} Oocysts shedding along the infection experiment, mean and 95% CI"}
plotOPGAlongInfSUM(ExpeDF_003)
```

## 3. Comparison host/parasite proxy

```{r plotComp3, echo=FALSE, warning=FALSE, fig.width = 12, fig.height = 10, fig.cap="\\label{fig:plotComp3} Weight as a function of OPG"}
plotCompOPGWeight(ExpeDF_003, ylim = c(90, 115))
```

# Expe_004, June 2018, second batch Parental strains (F0) BUSNA, STRA, SCHUNT, PWD, infection with Eferrisi (E64 and E139)

## 1. Weight loss

```{r weightalong4, echo=FALSE, warning=FALSE, fig.width = 12, fig.height = 10, fig.cap="\\label{fig:weightalong4} Weight along the infection experiment"}
plotWeightAlongInf(ExpeDF_004, ylim = c(90, 115))
```

```{r weightalongsum4, echo=FALSE, warning=FALSE, fig.width = 12, fig.height = 10, fig.cap="\\label{fig:weightalongsum4} Weight along the infection experiment, mean and 95% CI"}
plotWeightAlongInfSUM(ExpeDF_004, ylim = c(85, 120))
```

## 2. Parasite shedding
